---
title: WorldTempus Advent Calendar 2018
author: Dave Bloom
date: '2019-01-31'
slug: world-tempus-advent-calendar-2018
categories:
  - R
  - web scraping
  - EDA
  - network analysis
tags:
  - EDA
description: ''
featured: 'cover-avent_crop.png'
featuredalt: ''
featuredpath: 'img/main'
linktitle: ''
type: post
---

# Introduction

I love watches! For many, it is a dying (or dead) art. We can tell time using phones, computers, and smart watches, and they each perform many more functions making the traditional watch all but obsolete. But, to me, mechanical watches are the perfect example of form and function. I find it amazing how a selection of tiny gears and a long spring can measure something like time with very reasonable accuracy. 

As a result, I enjoy reading and watching horological content and, well, entering the occasional contest. So when WorldTempus had their annual advent calendar contest, I entered whenever I saw something of interest. Sometime after Christmas, they announced the winners on their [web site](http://en.worldtempus.com/article/events/arts-and-culture/advent-calendar-here-are-the-winners-26936.html?utm_source=Worldtempus+Concours+EN&utm_campaign=d835784c43-EMAIL_CAMPAIGN_2018_avent_gagnant_generale_EN&utm_medium=email&utm_term=0_1b496ba624-d835784c43-119672677) and I was immediately struck by how many winners were from France. I wondered what else I could glean from the small amount of data on that page so I set off to learn how to use rvest to scrape the data and regular expressions to clean and parse it. I also had the idea to visualize how some features are related and finally learned how to construct a simple Sankey diagram. 
</br></br>

# Setup
First step is to load in some libraries and set up some aesthetics.

```{r setup, message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(lubridate)
library(rvest)
library(networkD3)

my_font <- "Comfortaa"
my_bkgd <- "#f5f5f2"
my_theme <- theme(text = element_text(family = my_font, color = "#22211d"),
                  rect = element_rect(fill = my_bkgd), 
                  plot.background = element_rect(fill = my_bkgd, color = NA), 
                  panel.background = element_rect(fill = my_bkgd, color = NA), 
                  panel.border = element_blank(),
                  legend.background = element_rect(fill = my_bkgd, color = NA),
                  legend.key = element_rect(fill = my_bkgd),
                  plot.caption = element_text(size = 6))

theme_set(theme_light() + my_theme)

```
</br>

## Scraping the web
Below I use rvest's read_html function to load the url. The content is parsed using html_nodes that I identified using the SelectorGadget browser plugin. 

```{r}

url <- "http://en.worldtempus.com/article/events/arts-and-culture/advent-calendar-here-are-the-winners-26936.html?utm_source=Worldtempus+Concours+EN&utm_campaign=d835784c43-EMAIL_CAMPAIGN_2018_avent_gagnant_generale_EN&utm_medium=email&utm_term=0_1b496ba624-d835784c43-119672677"

df <- read_html(url) %>%
  html_nodes(".theContent , .theContent p , .theContent li") %>%
  html_text() 

# drop first two rows
df <- df[3:48] 

# view the top 10 rows
knitr::kable(head(df,10), format = "html")

```
Note that df is a single column with date and prize in one row and the winner and location in an alternating row. I'll deal with that in the next step.
</br></br>

## Data Cleaning and Munging
Cleaning the data and pulling out features (like 'Country' and 'Brand') required brushing up on regular expressions. It took some trial and error, but it was very good practice.

```{r}

# split single column of data into two columns
col1 <- character(length(df)/2)
col2 <- character(length(df)/2)
x <- 1
for (i in 1:length(df)) {
  if (i %% 2 == 0) {
    col1[x] <- df[i-1]
    col2[x] <- df[i]
    x <- x + 1
  }
}

data <- data.frame(col1,col2)

# create basic structure including the prize, winner's name, and date
data <- data %>%
  mutate(col3 = str_extract(col1, "\\d{2}.\\d{2}.\\d{4}"),
         col1 = str_remove(col1, "\\d{2}.\\d{2}.\\d{4}"),
         col1 = str_trim(str_remove(col1, "–"), side = "both"),
         col3 = dmy(col3)) 

# rename the columns to something useful
colnames(data) <- c("Prize","Winner","Date")

# helper function that splits out brand name from prize description
splitby <- function(x) {
  case_when(str_detect(x, " from ") ~ str_sub(x ,str_locate(x ," from ")[2]+1), 
            str_detect(x, " by ") ~ str_sub(x ,str_locate(x ," by ")[2]+1))
}

# create features from from data 
data <- data %>%
  mutate(City = str_match(Winner, "from ([a-zA-Z\\-\\é]+)")[,2],
         Country = str_match(Winner, "\\(([a-zA-Z\\-\\é ]+)\\)")[,2],
         Winner = str_match(Winner, "(.*) from")[,2],
         Brand = sapply(Prize, splitby))

# manual cleanup that general functions didn't catch
data$Brand[3] = "Louis Vuitton"
data$Brand[11] = "Ralph Lauren"

```


A quick view of the data to make sure it looks ok.

```{r paged.print=TRUE}

knitr::kable(head(data,10), format = "html")
```

</br></br>

### Which countries had the most contest winners? And what brands were most commonly offered as prizes?

```{r warning=FALSE}
 
data %>%
  add_count(Country, sort = T) %>%
  mutate(Country = fct_reorder(Country,n)) %>%
  ggplot(aes(Country, fill=Brand)) +
  geom_histogram(stat="count") +
  coord_flip() +
  labs(x="",y="") +
  theme(axis.text = element_text(size = 14),
        legend.position = c(0.75,0.3),
        legend.text = element_text(size=6)) +
  guides(fill = guide_legend(ncol = 2, keywidth = 1, keyheight = 1))

```

From the histogram, we see that nearly half of the winners are from France and about 20% are from the UK. However, with 18 brands, it's very difficult to answer my second question above. I'm still curious about how the brands are distributed among countries so I'll experiment with network analysis in the next section.
</br></br>

### What is the relationship between countries and brands?

```{r}

network_data <- data %>% select(Country, Brand) 

simpleNetwork(network_data, fontSize = 14, fontFamily = my_font, opacity = 0.8, linkDistance = 100, charge = -10, zoom = F)

```
This diagram certainly helps identify conenctions between counrties and brands, but it's not ideal. 
</br></br>

### Can I build a cleaner visualization of this relationship? 
I think a Sankey diagram would work well here, but I've never successfully built one before. 

```{r}

# building dataframes to help construct the Sankey diagram
nodes <- data %>%
  count(Country, sort = T) %>%
  mutate(node = seq(0, n_distinct(Country) - 1)) # this basically numbers each row 0 to 7

targets <- data %>%
  count(Brand, sort=T) %>%
  mutate(node = seq(n_distinct(data$Country), n_distinct(data$Country) + n_distinct(Brand) - 1)) # numbers rows 8 to 25

links <- data %>%
  select(Country, Brand) %>%
  left_join(nodes, by = "Country") %>%
  left_join(targets, by = "Brand") %>%
  select(source = node.x, target = node.y ) %>%
  mutate(value = 1) %>%
  arrange(source)

names <- data.frame(node = seq(0, n_distinct(data$Country) + n_distinct(data$Brand) - 1)) %>%
  left_join(nodes, by = "node") %>%
  select(node, Country) %>%
  left_join(targets, by = "node") %>%
  mutate(name = if_else(is.na(Country),Brand,Country)) %>%
  select(node, name) 
  
  
```


```{r}

# create sankey chart using Network3D
sankeyNetwork(Links = links, Nodes = names, Source = "source",
              Target = "target", Value = "value", NodeID = "name",
              colourScale = JS("d3.scaleOrdinal(d3.schemeCategory20);"),
              fontSize = 12, fontFamily = my_font, nodeWidth = 50, nodePadding	= 2)
```

I'm glad I put the extra effort into learning how to create this chart. I definitely learned a lot!

I think the simple Sankey diagram above does a very nice job of clearly visualizing the distribution of winners by country and brand. We clearly see that most of the winners were from France, the UK, and Belgium. We also see that products from Louis Vuitton, Omega, Carl F Bucherer, and Bovet were among the more popular brands offered as prizes. Additionally, brands that were offered more than once were distributed equally among France and the UK, with the exception of Louis Vuitton, which was distributed among France, the UK, and Belgium.